---
title: "Bootstraping_Regrission"
output:
  pdf_document: default
  html_notebook: default
---

# a) Bootstrapping

## 1)

```{r}
data = airquality$Solar.R
boot_sample = as.list(as.data.frame(replicate(1000, sample(data, 500, replace = T))))
med_sample = (sapply(boot_sample, median, na.rm = T))
```

## 2)

We simply delete first and last 5% of data, remaining data represent the 90% confidence interval.

```{r}
quantile(med_sample, c(0.05, 0.95))
```

## 3)

```{r}
med = median(med_sample)
se = sd(med_sample)
err = qt(0.9, length(med_sample) - 1)
ci = c(med - se * err, med + se * err)
ci
```

## 4)

Those are almost equal, I prefer second method

## 5)

There is a problem in loading inference.

# b) Simulation

## 6)

```{r}
library(msme)
library(COUNT)
ships$Risk <- ifelse(ships$incidents < 10, 'Low', 'High')
```

## 7)

Yes, it does.

But I can't perform a simulation ;-(

## 8)

No, it isn't. It is obvious which type B ships count as High Risk ships.

conditions are not satisfied, we need a sample which size be at least 30.

# c) Linear Regression, Multiple Linear Regression

## 9)

There is probably a relation between these two variables, but it isn't obvious in this plot. I think it's not possible to say that just by looking at the plot.

```{r}
library(mosaicData)
plot(Galton$height, Galton$father)
```

## 10)

These variables have low correlation so, we couldn't say that there is a strong relation.

```{r}
cor(Galton$height, Galton$father)
```

## 11)

It's showing that how much height of father impacts on child height.

```{r}
lm(Galton$height ~ Galton$father, data = Galton)
```

## 12)

height = 0.3994 \* father + 39.1104

Intercept is actually intercept of line equation.

## 13)

```{r}
father <- data.frame(father = c(70, 75, 80))
predict(lm(height ~ father, data = Galton), father)
```

## 14)

```{r}
lm(height ~ father + mother, data = Galton)
Galton
```

## 15)

normal distribution of residuals

```{r}
mlr <- lm(height ~ father + mother, data = Galton)
residuals = Galton$height - predict(mlr, Galton)
hist(residuals)
```

## 16)

normal distribution of resudals

```{r}
qqplot(residuals, rnorm(length(residuals)))
```

## 17)

Linearity

```{r}
plot(residuals, Galton$father)
plot(residuals, Galton$mother)
```

## 18)

constant variablity

```{r}
plot(residuals)
```

## 19 & 20)

It is statistically significant

```{r}
lm(height ~ father + mother + sex, data = Galton)
```

## 21)

By this method, we can just remove nkids.

As you can see residuals distribution is almost normal and they have constant variability.

relation between response variable and explanatory variables are linear.

```{r}
lmr = lm(height ~father + mother + sex, data = Galton)
residuals = Galton$height - predict(lmr, Galton)
hist(residuals)
plot(residuals)
```

# d) Logistic Regression

## 22)

```{r}
library(tidyr)
library(COUNT)
data("titanic")
titanic$survived <- ifelse(titanic$survived == 'yes', T, F)
eq <- glm(survived ~ ., data = titanic, family = binomial(link = 'logit'))
summary(eq)
```

## 23)

```{r}
head(titanic)
smpl = data.frame(class = c('2nd class'), age = 'adults', sex = 'man')
predict(eq, smpl, type = 'response')
```

## 24)

```{r}
titanic <- droplevels(titanic)
smpl <- titanic %>% expand(class, age, sex)
smpl
smpl$probabilty <- predict(eq, smpl, type = 'response')
smpl
```

## 25)

```{r}
titanic$predicted_survied <- ifelse(predict(eq, titanic, type = 'response') >= 0.5, T, F)
sum(titanic$survived == titanic$predicted_survied)
sum(titanic$survived == titanic$predicted_survied) / length(titanic$survived)

```

## 26)

No, it isn't valid, because there should be a lot of equipment to prevent people from dying in the sea after the Titanic accident.

If these two accidents happened at the same time and with the same available equipment, we could predict the number of survivors of second accident by using first accident's data.
