---
title: "Lab 1"
output:
  pdf_document: default
  html_notebook: default
---

# a) Variables and Types

## 1:

There is no difference

## 2:

logical, integer, real, complex, string,

## 3:

```{r}
4 + T
```

```{r}
#4 + "false"
```

## 4:

sum is not int the boolean format because '+' is an operation for numeric data types.

```{r}
sum <- T + F
sum
typeof(sum)
sum <- as.logical(sum)
typeof(sum)
sum
```

# b) Data structures

## 5:

Vector, list, matrix, data frame, factors

# c) Vectors

## 6:

```{r}
vec <- c(1, 2, 3)
vec
```

## 7:

We can't put variables of different types in a vector, since a vector is a random variable, so all variables in a vector must have the same type.

## 8:

```{r}
feature_1 <- c(50 : 250)
feature_1
```

## 9:

```{r}
length(feature_1)
```

## 10:

```{r}
mean(feature_1)
var(feature_1)
sd(feature_1)
median(feature_1)
```

## 11:

```{r}
plot(feature_1)
```

## 12:

```{r}
a <- feature_1[6 : 22]
a
```

## 13:

```{r}
b <- feature_1[c(6, 13, 21, 22, 43)]
b
```

## 14:

```{r}
c <- c(a, b)
c
```

## 15:

```{r}
find_a <- function(str){
  return (grepl("a", str))
}

str <- c("joey", "phoebe", "monica", "chandler", "ross", "rachel")
sum(as.integer(lapply(str, find_a)))

```

# d) Factors

## 16:

Factor in R is **a variable used to categorize and store the data, having a limited number of different values**.

Factors have limited number of different values, while vectors don't have any limitation.

```{r}
directions <- c("West", "East", "East", "North", "West", "West")
feature_2 <- factor (directions)
```

## 17:

It isn't possible, because 'South' isn't one of feature_2's levels.

## 18:

```{r}
levels(feature_2) <- c(levels(feature_2), "South")
feature_2
```

## 19:

There is nothing important to report, everything works well.

```{r}
feature_2[1] <- "South"
feature_2
```

# e) Missing values

## 20:

NA

## 21:

```{r}
feature_1[1] <- NA
feature_1
```

## 22:

mean() function can't calculate feature_1's mean and returns NaN because first element of this vector is missing.

We can set "na.rm" argument, true in mean() function to resolve this problem.

```{r}
mean(feature_1, na.rm = T)
```

## 23:

```{r}
feature_1[43] <- NA
which(is.na(feature_1))
```

## 24:

**NULL represents the null object in R**. NULL is used mainly to represent the lists with zero length, and is often returned by expressions and functions whose value is undefined.

# f) Lists

## 25:

List is a list of variables which types could be different.

## 26:

list [x] will return a list which only contains the x_th element of list, while list [[x]] will return x_th element of list, it self.

```{r}
lst <- list(4, 5, 6, list(7, 8, "xyz"))
```

# g) Naming

```{r}
named_list <- list(a = 1, b = 2, c = 3, d = c(4, 5, 6, 7))
```

## 27:

First one returns a list contains 2, while other ones returns 2 itself.

it is a syntax sugar for [[]] because they both do the same thing.

```{r}
named_list["b"]

```

```{r}
named_list[["b"]]
```

```{r}
named_list$b

```

# h) Data Frames

## 28:

```{r}
ncol(Orange)
```

## 29:

```{r}
nrow(Orange)
```

## 30:

```{r}
f3 <- Orange$circumference
f3_tmp <- Orange[[3]]
```

## 31:

f3 is a vector.

Due to the dipersion of circumference feature, this data set had been chosen randomly.

```{r}
table(f3)
```

## 32:

Tree feature is catagorical

```{r}
str(Orange)
```

## 33:

```{r}
s29 <- Orange[29, ]
s29
```

## 34:

It is a data frame with one row.

## 35:

```{r}
Orange[c(Orange$Tree == 3), ]
```

## 36:

```{r}
tmp <- Orange[1 : 10, c("Tree", "age")]
tmp
```

## 37:

```{r}
median(Orange$age)
```

# i) Export and Import

## 38:

```{r}
df_1 <- tail(Orange, n = 15)

```

## 39:

```{r}
write.csv(df_1, "df_1.csv", row.names = F)
```

## 40:

```{r}
df_2 <- read.csv("df_1.csv")
df_2
```
